### 2016-06-21 config/styles.inc.tex
Improve some figures

\pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
\pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
\pgfplotsset{existing/.style={color=existing}}
\pgfplotsset{LPMTruncInit/.style={color=LPMTruncInit,densely dashed}}
\pgfplotsset{LPMTrunc/.style={color=LPMTrunc}}
\pgfplotsset{RFIRInit/.style={color=RFIRInit,densely dashed}}
\pgfplotsset{RFIR/.style={color=RFIR}}
\pgfplotsset{best/.style={color=best}}

>>>>

\pgfplotsset{finalmodel/.append style={line width=0.75pt}}
\pgfplotsset{initmodel/.append style={line width=0.75pt}}

\pgfplotsset{GVXI/.style={color=GVXI,line width=1pt}}
\pgfplotsset{G0Hat/.style={color=G0Hat,line width=1.5pt}}
\pgfplotsset{existing/.style={finalmodel,color=existing}}
\pgfplotsset{LPMTruncInit/.style={initmodel,color=LPMTruncInit,densely dashed}}
\pgfplotsset{LPMTrunc/.style={finalmodel,color=LPMTrunc}}
\pgfplotsset{RFIRInit/.style={initmodel,color=RFIRInit,densely dashed}}
\pgfplotsset{RFIR/.style={finalmodel,color=RFIR}}
\pgfplotsset{best/.style={finalmodel,color=best}}
